Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
Remove brackets from var names and fix var names

i_sex <- c("male", "female")
i_measure <- c("deaths", "ylds (years lived with disability)")

@@

    data <- filter(GBDGL, measure == i_measure, sex == i_sex, cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate) 
    assign(paste(i_sex, i_measure, "interpolated_data", sep = " "), data)
x=data$age_cat
y=log(data$one_rate)

interpolated <- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
assign(paste(i_sex, i_measure, "interpolated", sep = " "), interpolated)
plot(x,y)

>>>>

i_sex <- c("male", "female")
i_measure <- c("deaths", "ylds") #" (years lived with disability)")

@@

    #print(paste(sex, measure, "interpolated_data", sep = "_"))
    #print(paste(sex, measure, "interpolated", sep = "_"))

    data <- filter(GBDGL, measure == i_measure, sex == sex, cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate) 
    assign(paste(sex, measure, "interpolated_data", sep = "_"), data)
x=data$age_cat
y=log(data$one_rate)

interpolated <- as.data.frame(spline(x, y, n = 5 *length (x), xmin = min(x-2), xmax = max(x + 2)))
interpolated$y <- exp(y)
assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(x,y)
